---
title: "HelloDataIntro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HelloDataIntro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(HelloData)
```

## How to use this package
This package provides an easy introduction to any new data set.

Lets take the below simplistic data set.
```{r}
first_column <- rep("A",10)
second_column <- runif(n=10, min=1, max=20)
third_column <- c(1,2,NA,NA,5,6,7,8,9,10)
df <- data.frame(first_column, second_column, third_column)
```

The first function returns basic information about the data set.
```{r}
intro(df)
```
Now we know how many columns and rows there are in a human readable format.


The second function expands on the first with more information on the columns.
```{r}
intro_columns(df)
```
The third function identifies any row with missing values.
```{r}
rows_with_missing_values(df)
```

The fourth function expands on the third by identifying which columns have missing values.

```{r}
missing_values_by_column(df)
```

The final function provides histograms for all numeric variables.
```{r}
histograms(df)
```

